
```{r}
library(pantomime)
library(seqhelp)
library(tidyverse)
```

Going with the primers and probe from Faveri et al. 2009 and the Gblock from this as well. 


Forward primer: 
CGCCTGTGAGTATCTCTCGA

```{r}
fwdp <- "CGCCTGTGAGTATCTCTCGA"
```

Reverse primer: 
GTTGAAGAGAAGAATCGCGTGAT
reverse_complement:
ATCACGCGATTCTTCTCTTCAAC

```{r}
revp<- "GTTGAAGAGAAGAATCGCGTGAT"
```

Sequence from Blast:

MK253305.1 is perkinsus marinus, I found it by blasting the primer sequence from Faveri et al 2009

```{r}
permar<-read_fasta(here::here("data","raw","MK253305.1.fasta"))
```

# Save amplicon sequence -- between the forward primer and end of reverse primer

".*? matches any character (non-greedy) in between"

```{r}
permar <- permar %>%
  mutate(amplicon = str_extract(seq, "CGCCTGTGAGTATCTCTCGA.*?ATCACGCGATTCTTCTCTTCAAC"))
nchar(permar$amplicon)
```

# Save glbock sequence

Find thirteen characters before forward primer 

```{r}
before = str_extract(permar$seq, ".{18}(?=CGCCTGTGAGTATCTCTCGA)")
after = str_extract(permar$seq, "(?<=ATCACGCGATTCTTCTCTTCAAC).{18}")
```

```{r}
permar <- permar %>%
  mutate(gblock = str_extract(seq, "CCTCCGAAAGGAGGCTTG.*?GCATTACGTCAAATCTAT"))
```

```{r}
str(permar$gblock)
nchar(permar$gblock)
nchar(permar$amplicon)
full<-permar$seq
```


```{r}
seqhelp::write_fasta(here::here("out","pmar_fwd.fasta"),"F",fwdp)
seqhelp::write_fasta(here::here("out","pmar_rev.fasta"),"R",revp)
seqhelp::write_fasta(here::here("out","pmar_gblock.fasta"),"gblock",permar$gblock)
seqhelp::write_fasta(here::here("out","pmar_probe.fasta"),"probe","CGCAAACTCGACTGTGTTGTGGTG")

probe_info<-tibble(full_probe_info= "5’-/56-FAM/CGC AAA CTC GAC TGT GTT GTG GTG/3BHQ1/-3'")

write_csv(probe_info, here::here("out","full_probe_info.csv"))

examine<-read_fasta(here::here("out","pmar_fwd.fasta"))
```

