


```{r}
install.packages("rsconnect")
```


```{r}
rsconnect::setAccountInfo(name='jlmatt', token='CF0F0546C228B16332012F12284CE016', secret='8kP1MxDsTsm9rbkreoylzpXn+RXz1y1QnbDaIVuK')
```

```{r}
Sys.setenv(RENV_CONFIG_ENABLED = "FALSE")
rsconnect::deployApp("shiny")
```

Didn't work, try this

```{r}

install.packages(c("fastmap","htmltools"))
install.packages("sass")
install.packages(c("bslib","cachem","cpp11","tzdb","shiny"))
```

Now it's working I think 

but the graphs didn't load

```{r}
rsconnect::showLogs(appName = "shiny", account = "jlmatt", streaming = TRUE)
```



Everything below was trying to use shiny live, which was a mess.







```{r}
library(here)
```


```{r, eval = FALSE}
install.packages(c("shinylive","httr2","curl","openssl","jsonlite"))
```

```{r, eval = FALSE}
packageVersion("shinylive")
packageVersion("httr2")
```

```{r, eval = FALSE}
install.packages(c("httr2", "curl", "openssl"))  # from CRAN
```

```{r}
appdir <- here::here("shiny")
destdir <- here::here("docs") 
```

```{r}
shinylive::export(appdir = appdir, destdir = destdir)
```

hit an error, so going to do this

```{r}
remove.packages("dplyr")
install.packages("dplyr") 
```

hit another error, "Error in desc$Repository : $ operator is invalid for atomic vectors"

try this and some minor adjustments to the top of the app.R file (change which packages are loaded and change how the data is loaded in)
```{r, eval =FALSE}
install.packages(c(
  "shiny","bslib","ggplot2",
  "dplyr","tidyr","readr","purrr","stringr","tibble",  # core tidyverse pieces
  "here","leaflet","plotly","shinyscreenshot"
))
```

Ok, had issues with the page loading, so added a .nojeylkk file, now doing this:

```{r}
install.packages("pak")
pak::pak(c(
  "ggplot2","scales","withr","rlang","vctrs","gtable","isoband",
  "MASS","mgcv","tibble","cli","glue","digest","farver","labeling","lifecycle"
))
```

