---
title: "23_qPCR_std_curve_results"
format: html
---

Want to assess the standard curve results from the three qPCR runs.

```{r}
library(here)
library(tidyverse)
library(googledrive)
```


```{r, eval = FALSE}
drive_download("cvir_qpcr24_dermo_runs_std_curve",
  path = here::here("data","raw","cvir_qpcr24_dermo_runs_std_curve.xlsx"),
  type = "xlsx",
  overwrite = TRUE
)

drive_download("cvir_qpcr24_dermo_runs_std_curve_exp",
  path = here::here("data","raw","cvir_qpcr24_dermo_runs_std_curve_exp.xlsx"),
  type = "xlsx",
  overwrite = TRUE
)
```

```{r}
data <- readxl::read_xlsx(here::here("data","raw","cvir_qpcr24_dermo_runs_std_curve.xlsx"))

exp <- readxl::read_xlsx(here::here("data","raw","cvir_qpcr24_dermo_runs_std_curve_exp.xlsx"))
```

```{r}
data <- data %>%
  left_join(exp, by = "dilution")
```

```{r}
str(data)
```


# Run 1

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "05.15.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope1 <- coef(mod)[["log_10_conc"]]

efficiency1 <- (10^(-1 / slope1) - 1) * 100
```

Calculate R square
```{r}
rsquare1 <- summary(mod)$r.squared
```

Ok, so this run is money!

# Run 2

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "07.27.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope2 <- coef(mod)[["log_10_conc"]]

efficiency2 <- (10^(-1 / slope2) - 1) * 100

efficiency2
```

Calculate R square
```{r}
rsquare2 <- summary(mod)$r.squared
```

This run is bad!

# Run 3

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "09.15.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope3 <- coef(mod)[["log_10_conc"]]

efficiency3 <- (10^(-1 / slope3) - 1) * 100

efficiency3
```

Calculate R square
```{r}
rsquare3 <- summary(mod)$r.squared
```

# Run 4

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "09.23.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope4 <- coef(mod)[["log_10_conc"]]

efficiency4 <- (10^(-1 / slope4) - 1) * 100

efficiency4
```

Calculate R square
```{r}
rsquare4 <- summary(mod)$r.squared
```


# Take out last dilution


Let's do this but remove dilution 13 (lower detection)

```{r}
data <- data %>%
  filter(!dilution == "gb_13_te")
```

# Run 1

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "05.15.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope1_ld <- coef(mod)[["log_10_conc"]]

efficiency1_ld <- (10^(-1 / slope1_ld) - 1) * 100
```

Calculate R square
```{r}
rsquare1_ld <- summary(mod)$r.squared
```

Ok, so this run is money!

# Run 3

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "09.15.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope3_ld <- coef(mod)[["log_10_conc"]]

efficiency3_ld <- (10^(-1 / slope3_ld) - 1) * 100

efficiency3_ld
```

Calculate R square
```{r}
rsquare3_ld <- summary(mod)$r.squared
```

Slightly brings down the efficiency for the latest run

# Run 4

```{r}
mod <- lm(average_ct ~ log_10_conc, data = data %>% filter(date == "09.23.26"))
```

Slope
```{r}
coef(mod)
```

Calculate efficiency
```{r}
slope4_ld <- coef(mod)[["log_10_conc"]]

efficiency4_ld <- (10^(-1 / slope4_ld) - 1) * 100

efficiency4_ld
```

Calculate R square
```{r}
rsquare4_ld <- summary(mod)$r.squared
```

```{r}

```

