
Make sure you are in the shiny environment in /home/jmatt1/bin/miniforge3/bin/mamba

```{r}
library("shiny")
library("bslib")
library("ragg")

runExample("01_hello")
```

```{r}
runApp("shiny")
```

# Adjust data

The data for the shiny app was copied from data/derived.  Need to make a few tweaks that are in the graphing examination markdown. 

```{r}
data <- readRDS(here::here("data","derived","clean_data.RDS"))
```

Take out IND data, doesn't add anything

```{r}
data <- data %>%
  filter(!sample_site == "IND")
```

Save data

```{r}
data <- saveRDS(data,here::here("shiny","data","clean_data.rds"))
```

Resources: 
https://shiny.posit.co/r/gallery/widgets/widget-gallery/


Ways to improve the graph: 
 1) Need a way to specify that oysters were collected but no females found 
 2) How can I do this with a better set of symbols and colors and background
 3) need to order the checkbox on the left in order of latitude
 4) need to fix the legends so they are visible
 5)     each site is either a square or a triangle, but the color x shape combo is how it            works
          so the first legend would be color
          the second legend would be site with either square or triangle (this legend could be hidden with a click on the shiny app)

Probably need to specify that you need to fill for the bay, then backcode the legend description somehowx


Some other notes: 
limits: This argument controls the order of the factor levels in the plot. limits is used to set the factor levels that will be included and their order. It affects both the plot and the legend.
